---
title: "p8105_hw1_yh3094"
author: "Yun He"
date: "September 16, 2018"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

# Problem 1

The chunk below creates a data frame with different variable types and tests the function `mean()`.

```{r p1_df_create}
p1_df = tibble(
  vec_numeric = runif(10, 0, 5),
  vec_logical = vec_numeric > 2,
  vec_char = c("I", "am", "now", "creating", "a", "vector", "whose", "length", "is", "10"),
  vec_factor = factor(c("Female", "Male", "Male", "Male", "Male", "Male", 
               "Female", "Female", "Female", "Female"))
)

mean(p1_df$vec_numeric)
mean(p1_df$vec_logical)
mean(p1_df$vec_char)
mean(p1_df$vec_factor)
```

When taking the mean of each variable in my dataframe, it works for numeric and logical factors and doesn't work for character and factor vectors.

The chunk below applies the `as.numeric` function to the logical, character, and factor variables.

```{r p1_as_numeric, eval=FALSE}
as.numeric(p1_df$vec_logical)
as.numeric((p1_df$vec_char))
as.numeric(p1_df$vec_factor)
```

The chunk below converts the character variable from character to factor to numeric, and converts the factor variable from factor to character to numeric.

```{r p1_class_conversion}
as.numeric(factor(p1_df$vec_char))
as.numeric(as.character(p1_df$vec_factor))
```

# Problem 2

The chunk below creates a new data frame.

```{r p2_df_create}
set.seed(1234)

p2_df = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  p2_vec_logical = (x + y) > 0,
  p2_vec_numeric = as.numeric(p2_vec_logical),
  p2_vec_factor = factor(p2_vec_logical)
)
```

The size of the datset `p2_df` is `r nrow(p2_df)` rows and `r ncol(p2_df)` columns. 
The mean and median of `x` is `r mean(p2_df$x)` and `r median(p2_df$x)`, respectively.
The proportion of cases for which the logical vector is TRUE is `r round(sum(p2_df$p2_vec_numeric)/1000, digits=2)`.

The chunk below makes a scatterplot of `y` vs `x` with color points using the logical variable.

```{r p2_yx_scatter_logical}
ggplot(
  
)
```


