---
title: "p8105_hw1_yh3094"
author: "Yun He"
date: "September 16, 2018"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

# Problem 1

## Create a data frame

The chunk below creates a data frame with different variable types and tests the function `mean()`.

```{r p1_df_create}
p1_df = tibble(
  vec_numeric = runif(10, 0, 5),
  vec_logical = vec_numeric > 2,
  vec_char = c("I", "am", "now", "creating", "a", "vector", "whose", "length", "is", "10"),
  vec_factor = factor(c("Female", "Male", "Male", "Male", "Male", "Male", 
               "Female", "Female", "Female", "Female"))
)

mean(p1_df$vec_numeric)
mean(p1_df$vec_logical)
mean(p1_df$vec_char)
mean(p1_df$vec_factor)
```

### Comments on the results

When taking the mean of each variable in my dataframe, it works for numeric and logical factors, and doesn't work for character and factor vectors. Because regarding the `x` in the function `mean(x, ...)`, it says currently there are only methods for numeric/logical vectors and date, date-time and time interval objects.

## Application of the `as.numeric` function 

The chunk below applies the `as.numeric` function to the logical, character, and factor variables.

```{r p1_as_numeric, eval=FALSE}
as.numeric(p1_df$vec_logical)
as.numeric(p1_df$vec_char)
as.numeric(p1_df$vec_factor)
```

### Comments on the results

The logical and factor vectors can be converted to numeric vectors, while the character vector can't. 

## Convert Variable types

The chunk below converts the character variable from character to factor to numeric, and converts the factor variable from factor to character to numeric.

```{r p1_conversion}
as.numeric(as.factor(p1_df$vec_char))
as.numeric(as.character(p1_df$vec_factor))
```

### Comments on the results

The character variable can be converted from character to factor to numeric, while the factor variable can't be converted from factor to character to numeric. Because character vectors can't be converted to numeric vectors. 

# Problem 2

## Create a data frame

The chunk below creates a new data frame for problem 2.

```{r p2_df_create}
set.seed(1234)

p2_df = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  p2_vec_logical = (x + y) > 0,
  p2_vec_numeric = as.numeric(p2_vec_logical),
  p2_vec_factor = as.factor(p2_vec_logical)
)
```

## Describe vectors using inline R code

The size of the dataset `p2_df` is `r nrow(p2_df)` rows and `r ncol(p2_df)` columns. 
The mean and median of `x` is `r mean(p2_df$x)` and `r median(p2_df$x)`, respectively.
The proportion of cases for which the logical vector is TRUE is `r round(sum(p2_df$p2_vec_numeric)/1000, digits=2)`.

## Make scatterplots of `y` vs `x` with color points using different variable types

The chunk below makes a scatterplot of `y` vs `x` with color points using the logical variable.

```{r p2_yx_scatter_logical}
yx_scatter_logical = ggplot(p2_df, aes(x, y, color = p2_vec_logical)) + geom_point()
yx_scatter_logical
```

The chunk below makes a scatterplot of `y` vs `x` with color points using the numeric variable.

```{r p2_yx_scatter_numeric}
yx_scatter_numeric = ggplot(p2_df, aes(x, y, color = p2_vec_numeric)) + geom_point()
yx_scatter_numeric
```

The chunk below makes a scatterplot of `y` vs `x` with color points using the factor variable.

```{r p2_yx_scatter_factor}
yx_scatter_factor = ggplot(p2_df, aes(x, y, color = p2_vec_factor)) + geom_point()
yx_scatter_factor
```

## Export the first scatterplot

The chunk below exports the first scatterplot to my project directory using `ggsave`.

```{r yx_scatter_logical_export}
ggsave("yx_scatter_logical.pdf", plot = yx_scatter_logical)
```

